---
title: "ESM 206 Lab 5"
author: "Logan Babcock"
date: "October 25, 2021"
output: 
  html_document: 
    theme: yeti
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages

library(tidyverse)
library(effsize)

```

#Creating a table of contents

## Part 1: Confidence intervals

In this section, we will use the `t.test()` function to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values then learn to ise `t.test()` to return confidence intervals, and learn about un-line code referenceing so our text becomes more reporducible too.
```{r}
# Create a mock sample

otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29)

# Find the confidence interval:

otter_ci <- t.test(otter_lengths)

# Find the Standard deviation

otter_sd <- sd(otter_lengths)

```
*Confidence interval of 29.1 and 44.67... 
means we would expect if we took multiple sample and made a 95% confidence for each, we would expect the true parameters (ex: true population mean) to be in 95% of them.*

**Bad Example** Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n= 8) with an 95% confidence interval of [29.2, 44.67] inches. 

#### Now, using in-line referencing

mean otter length is `r round(otter_ci$estimate, 1)` inches
