---
title: "ESM 206 Lab 5"
author: "Logan Babcock"
date: "October 25, 2021"
output: 
  html_document: 
    theme: yeti
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages

library(tidyverse)
library(effsize)

```

#Creating a table of contents

## Part 1: Confidence intervals

In this section, we will use the `t.test()` function to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values then learn to ise `t.test()` to return confidence intervals, and learn about un-line code referenceing so our text becomes more reporducible too.
```{r}
# Create a mock sample

otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29)

# Find the confidence interval:

otter_ci <- t.test(otter_lengths)

# Find the Standard deviation

otter_sd <- sd(otter_lengths)

```
*Confidence interval of 29.1 and 44.67... 
means we would expect if we took multiple sample and made a 95% confidence for each, we would expect the true parameters (ex: true population mean) to be in 95% of them.*

**Bad Example** Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n= 8) with an 95% confidence interval of [29.2, 44.67] inches. 

#### Now, using in-line referencing

mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [`r round(otter_ci$conf.int[1], 1) `, `r round(otter_ci$conf.int[2], 1)`]

## Part 2: Two sample t-tests

Make two mock samples and ask the wuestions : do we have suffucuent edicdnce to make us reject the null hypotohesis that these samples were drawn from populations with the same mean

```{r}
# Make the mock samples 
oak_trees <- c(20, 19, 24, 28, 34, 12, 15, 25)

pine_trees <- c(39, 36, 20, 37, 22, 19, 18)

# two sample t-test

tree_t <- t.test(oak_trees, pine_trees)
```

*p value means if these samples were taken from a pop with the same mean , then there is a 28.7% chance of taking samples from these populations and finding that the sample means are at least as different as the ones we found with random chance*

The mean hights of oak and pine trees were (X +- Y) and (X+-Y), respectivly, and the difference was not significant (t(`r tree_t$parameter`) = `r tree_t$statistic`, p = `r tree_t$p.value`).

"t(df) = t-statistic, p = p-value"

## Part 3: Antoher t-test with cars data

Looking to see if there is a significant difference in city MPG for compact cars and suv's
```{r}
# clean data

compact_suv <- mpg %>% 
  filter(class %in% c("compact", "suv"))

# check for the remaining levels

unique(compact_suv$class)

```

Create a histogram of city gas milage (cty) faceted by class starting from compact_suv.
```{r}
# making the graph, hostograms only need one axis variable

ggplot(data = compact_suv, aes(x = cty)) +
  #make it a histogram
  geom_histogram(bins = 12) +
  # divide it by class
  facet_wrap(~ class)

# make a quantile quantile plot (qq plot)

ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() + 
  facet_wrap (~class)
```

Find some summary statistics for each group. 
```{r}

# making a summary table 
car_stats <- compact_suv %>% 
  group_by(class) %>% 
  summarize(
    mean_city = mean(cty), 
    sd_city = sd(cty),
    sample_size = n()
  )
# view the table
car_stats
```

The t_test function REALLY wants vectors of things. Use the `pull()` funtion to get a vector from a data frame.
```{r}
# using the pull function on compact cars
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

# using pull function for SUVs
suv_sample <- compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)
```
H0: mean city gas mileages for SUV's and compact cars are the same
```{r}
t.test(compact_sample, suv_sample)
```
There is a signifacnt difference in mean city gas mileages between compact cars and suvs (typically would include t test statistic values here)

